Twisted \(M\)-theory and its perturbative quantization.

### 2022-09-29 omega.tex
merge

We consider the holomorphic two-form
\[
S(a,b,c) = a \, w_1 \d w_2 \wedge \d w_3 + b \, w_2 \d w_3 \wedge \d w_1 + c \, w_3 \d w_1 \wedge \d w_2 .
\]
In order for $S(a,b,c)$ to be $\del$-closed we have the following constraint on the variables $a,b,c$:
\beqn\label{eqn:abc}
a + b + c = 0 .
\eeqn
Using this equation, we can eliminate a single variable. 
We reparameterize using two new variables $a = \ep$, $b=\delta$, $c = -\ep - \delta$ and denote
\[
S(\vep, \delta) \define \ep \, w_1 \d w_2 \wedge \d w_3 + \delta \, w_2 \d w_3 \wedge \d w_1 - (\ep + \delta) \, w_3 \d w_1 \wedge \d w_2 .
\]

@@

@@

>>>>

We consider the holomorphic two-form
\[
S(a,b,c) = a \, w_1 \d w_2 \wedge \d w_3 + b \, w_2 \d w_3 \wedge \d w_1 + c \, w_3 \d w_1 \wedge \d w_2 .
\]
In order for $S(a,b,c)$ to be $\del$-closed we have the following constraint on the variables $a,b,c$:
\beqn\label{eqn:abc}
a + b + c = 0 .
\eeqn
Using this equation, we can eliminate a single variable. 
We reparameterize using two new variables $a = \ep$, $b=\delta$, $c = -\ep - \delta$ and denote
\[
S(\vep, \delta) \define \ep \, w_3 \d w_1 \wedge \d w_2 + \delta \, w_2 \d w_3 \wedge \d w_1 - (\ep + \delta) \, w_1 \d w_2 \wedge \d w_3 .
\]

@@

\subsection{Deformation of $M2$ and $M5$ branes}

We argue that when restricted to $M2$ and $M5$ branes that the supercharge $S(\ep, \delta)$ becomes explicit superconformal elements which live in the holomorphic twist of the relevant $3d$ and $6d$ superconformal algebras, respectively.

Let's first consider the $M2$ brane case. 
In the notation of this section, let us take the $M2$ brane to live along $z_1 = z_2 = w_1 = w_2 = 0$:
\[
\{0\} \times \{0\} \times \CC_{w_3} \times \RR_t \subset \CC^2_{z_i} \times  \CC^3_{w_a} \times \RR_t .
\]

Recall that the odd part of the 3-dimensional superconformal algebra, which can be identified with $\lie{osp}(6|1)$, is 
\[
\wedge^2 W \otimes R 
\]
where $W$ is the defining $\lie{sl}(4)$ representation and $R$ is the defining $\lie{sl}(2)$ representation. 
In \ref{s:m2embedding} we polarized $R$ and decomposed this as $(\wedge^2 W)_{+1} \oplus (\wedge^2 W)_{-1}$.

Along the brane, the first summand $(\wedge^2 W)_{+1}$ corresponds to the residual supertranslations in the twist of the 3d $\cN=8$ supersymmetry algebra. 
The second summand $(\wedge^2 W)_{-1}$ corresponds to residual superconformal transformations. 
It is spanned by elements of the form 
\[
w_3 \otimes (v_\alpha \wedge v_\beta)
\]
where $w_3$ is the holomorphic coordinate along the $M2$ brane and $\{v_\alpha\}$ is a basis for $W \cong \CC^4$.
In the notation of the 11-dimensional theory, $W$ is spanned by translation invariant holomorphic one-forms $\{\d z_1, \d z_2, \d w_1, \d w_2\}$.

Restricting the element $S(\ep,\delta)$ to the $M2$ brane we obtain precisely an element of this form: 
\[
S(\ep,\delta)|_{M2} = \ep w_3 \otimes (v_3 \wedge v_4).
\]
Notice that the dependence on $\delta$ has completely dropped since $\delta$ is proportional to terms involving the linear functions $w_1,w_2$ which are set to zero along the brane.

\parsec[]
Next, let's consider the restriction of the element $S(\ep, \delta)$ to an $M5$ brane.

We take the $M5$ brane to live along $z_2 = w_3 = t = 0$:
\[
\CC_{z_1} \times \{0\} \times \CC_{w_1} \times \CC_{w_2} \times \{0\} \subset \CC^2_{z_i} \times  \CC^3_{w_a} \times \RR_t .
\]

\brian{I'm using $R_{6d} = \CC.\d z_2 \oplus \CC. \d w_3$.}
Recall that the odd part of twist of the 6-dimensional superconformal algebra (which is also $\lie{osp}(6|1)$) can be identified with 
\[
L \otimes R \oplus \wedge^2 L \otimes R 
\]
where $L \cong \CC^3$ is the defining $\lie{sl}(3)$ representation and $R \cong \CC^2$ is the defining $\lie{sl}(2)$ representation. 
A basis for $L$ is given by the constant holomorphic one-forms along the brane, which in this notation is $\{\d z_1, \d w_1, \d w_3\}$. 
A basis $\{r_1,r_2\}$ for $R$ corresponds in 11-dimensions to the constant holomorphic one-forms $\{\d z_1, \d w_3\}$.

The first summand $L \otimes R$ corresponds to residual supertranslations of the 6d $\cN=(2,0)$ superconformal algebra after the holomorphic twist. 
The second summand $\wedge^2 \otimes R$ corresponds to residual superconformal elements.

Following our embedding from \S \ref{s:m5embedding} we find that the restriction of $S(\ep, \delta)$ is precisely one of these superconformal elements:
\[
S(\ep, \delta) = - \left(\delta w_2 \d w_1 + (\ep + \delta) w_1 \d w_2 \right) \otimes r_2 .
\]

@@

\subsection{Localization to 7d}

Consider
\[
S(\ep) = \ep (w_1 \d w_2 \wedge \d w_3 + w_2 \d w_1 \wedge \d w_3) .
\]

The annihilator of $[S(\ep),-]$ in $E(5,10)$ is linearly spanned by the following elements
\begin{itemize}
\item Divergence-free vector fields of the form $f_i(z_1,z_2, w_3) \del_{z_i}$. 
\item Vector fields of the form $(w_1 w_2)^n \del_{w_3}$. 
\item $\cdots$
\end{itemize}

### 2022-09-29 residual.tex
merge

% Created 2020-10-14 Wed 14:51
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{macros-mtheory}
\usepackage{cmupint}

@@

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}
\def\del{\partial}
\def\hotimes{\, \otimes \,}
\def\ep{\epsilon}
\def\div{\partial_{\Omega}}
\def\m2{\mathfrak{m}2\mathfrak{brane}}
\def\susy{\mathfrak{susy}}
\def\so{\mathfrak{so}}
\def\siso{\mathfrak{siso}}
\def\fsl{\mathfrak{sl}}
\def\lie#1{\ensuremath{\mathfrak{#1}}}

@@

\maketitle
\tableofcontents

@@

Recall, the (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
\[
  \ft_{11d} = V \oplus \Pi S
\]
where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
this decomposes into three irreducibles, 
\beqn\label{eqn:decomp}
  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
\eeqn
Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
The bracket in $\ft_{11d}$ is defined using the first projection
\[
[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
\]
The super Poincar\'{e} algebra is
\[
  \siso_{11d} = \so(11 , \CC) \ltimes \ft_{11d} .
\]
The $R$-symmetry is trivial in 11-dimensional supersymmetry.

We recall the so-called M2 brane central extension of the super Poincar\'e algebra.
Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.  
Let
\[
  \Gamma_{\wedge^2} : \Sym^2(S) \to \wedge^2 V \subset \Omega^2(\RR^{11}) 
\]
be the $\lie{so}(11,\CC)$-equivariant projection onto the $\wedge^2 V$ summand.

The super dg Lie algebra $\m2$ is the central extension of $\siso_{11d}$ by the cocycle
  \[
    c_{M2} \in \clie^2\left(\siso_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
  \]
  defined by the formula 
  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$ as in the decomposition \eqref{eqn:decomp}.

Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.
Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$ for which we use to perform the a holomorphic twist of 11-dimensional supergravity.  
We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.

Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
We can decompose the algebra into $\lie{sl}(5)$ representations, using the isomorphisms
\deq{
  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
}
As $\fsl(L) = \fsl(5)$-modules we have
\[
V = L \oplus L^\vee \oplus \CC_t
\]
and $\so(11, \CC)$ decomposes as
\[
\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
\]
Furthermore, the spinorial representation can be identified with
\[
S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
\]
The element $Q$ lives in the first summand.
Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.

@@

The cohomology of the non-centrally extended algebra was computed in \cite{SWpure}, we briefly recall the result. 
The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
So, as expected, of the translations only the holomorphic ones $L^\vee$ survive.
The map 
\[
[Q,-] \colon \lie{so}(11;\CC) \to S 
\] 
is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.

@@

In this section we compare to the work of ??.
In these references, the algebra $\m2$ is defined as an $L_\infty$  
central extension of $\siso_{11d}$.

@@

In \cite{CLsugra} it is shown how $D2k$ branes couple to type IIA supergravity in the twisted situation. 
We have already shown how the dimensional reduction of 11-dimensional supergravity along a holomorphic circle $S^1 \subset \CC^\times$ is equivalent to the $\SU(4)$ invariant twist of type IIA supergravity
\[
\CC^4 \times \RR^2 .
\]

>>>>

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory,amsaddr}

\addbibresource{cfs.bib}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

@@

@@

\maketitle
%\tableofcontents

@@

\paragraph{
Recall, the (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
\[
  \ft_{11d} = V \oplus \Pi S
\]
where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
this decomposes into three irreducibles, 
\beqn\label{eqn:decomp}
  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
\eeqn
Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
The bracket in $\ft_{11d}$ is defined using the first projection
\[
[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
\]
The super Poincar\'{e} algebra is
\[
  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
\]
The $R$-symmetry is trivial in 11-dimensional supersymmetry. }

\paragraph{
We recall the so-called M2 brane central extension of the super Poincar\'e algebra.
Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.  
Let
\[
  \Gamma_{\wedge^2} : \Sym^2(S) \to \wedge^2 V \subset \Omega^2(\RR^{11}) 
\]
be the $\lie{so}(11,\CC)$-equivariant projection onto the $\wedge^2 V$ summand.
The super dg Lie algebra $\m2$ is the central extension of $\lie{siso}_{11d}$ by the cocycle
  \[
    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
  \]
  defined by the formula 
  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$ as in the decomposition \eqref{eqn:decomp}. }

We view $\m2$ as a $\ZZ \times \ZZ/2$-graded Lie algebra where the differential is of bidegree $(1,+)$.
Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$ for which we use to perform the a holomorphic twist of 11-dimensional supergravity.  
We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.

\paragraph{
Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
\deq{
  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
}
Also, $\lie{so}(11, \CC)$ decomposes as
\[
\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
\]
Furthermore, the spinorial representation can be identified with
\[
S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
\]
The element $Q$ lives in the first summand.
Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$. }

@@

The cohomology of the non-centrally extended algebra was computed in \cite{SWpure}, we briefly recall the result. 
The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
So, as expected, of the translations only the holomorphic ones $L^\vee$ survive.
The map 
\[
[Q,-] \colon \lie{so}(11,\CC) \to S 
\] 
is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.

@@

In this section we compare to the work of ??.
In these references, the algebra $\m2$ is defined as an $L_\infty$  
central extension of $\lie{siso}_{11d}$.

@@

In \cite{CLsugra} it is shown how $D2k$ branes couple to type IIA supergravity in the twisted situation. 
We have already shown how the dimensional reduction of 11-dimensional supergravity along a holomorphic circle $S^1 \subset \CC^\times$ is equivalent to the $SU(4)$ invariant twist of type IIA supergravity
\[
\CC^4 \times \RR^2 .
\]
